---
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "# ",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# jsonify

jsonify converts a data.frame to JSON. 

### Aren't there already data.frame to JSON converters?

Yep.

### So why did you build this one?

Because I wanted it available at the source ( C++ ) level for integrating into other packages.

### Is it fast

It does alright

```{r}

library(microbenchmark)
library(jsonlite)

n <- 1e6
df <- data.frame(
  id = 1:n
  , value = sample(letters, size = n, replace = T)
  , val2 = rnorm(n = n)
  , log = sample(c(T,F), size = n, replace = T)
  #, dte = sample(seq(as.Date("2018-01-01"), as.Date("2018-01-31"), length.out = n), size = n, replace = T)
)

microbenchmark(
  jsonlite = {
    js <- jsonlite::toJSON( df )
  },
  jsonify = {
    js <- jsonify::to_json( df )
  },
  times = 5
)

```

### What doesn't it do?

Quite a lot, it's still in development!

### There's no 'Date' type in JSON, how have you handled this?

At the moment I haven't. At its core in R, `Dates` are numeric, so they're treated as numbers when convrted to JSON. 

I haven't fully decided how to handle dates yet.

```{r}
df <- data.frame(dte = as.Date("2018-01-01"))
jsonify::to_json( df )
```


### What do you mean by 'available at the source' ?

I want to be able to call the C++ code from another package, without going to & from R. Therefore, the C++ code is imlemented in headers, so you can `LinkTo` it in your own package. 

For example, the LinkingTo section in DESCRIPTION will look something like

```r
LinkingTo: 
    Rcpp,
    jsonify
```
And in a c++ source file so you can `#include` the header and use the available functions

```c++
#include "jsonify.hpp"
// [[Rcpp::depends(jsonify)]]

Rcpp::StringVector my_json( Rcpp::DataFrame df ) {
  return jsonify::to_json( df );
}
```

### Can I call it from R if I want to?

Yes. 

```{r}
df <- data.frame(
  id = 1:3
  , val = letters[1:3]
  , stringsAsFactors = FALSE 
  )
jsonify::to_json( df )
```

### How do I install it?

Install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("SymbolixAU/jsonify")
```
